\Rpackage{MSnbase} development

### 2012-02-03 inst/doc/Foreword.tex
Update vignette with 'combine' section + minor fixes.
CHANGES IN VERSION 1.3.9
-------------------------
 o updated demo vignette <2012-02-03 Fri>
 o sorting numeric subsets in "[" pSet, as unsorted 
   numerical indexes fails  <2012-02-03 Fri>
 o Added match.arg in combineFeatures so that 
   a unique default value (the first) is used when no 
   fun is specified <2012-02-03 Fri>




git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@62533 bc3139a8-67e5-0310-9ffc-ced21a209358

\Rpackage{MSnbase} is in an early development %%(package version \Sexpr{packageVersion("MSnbase")}, 
(see section \ref{sec:sessionInfo} for details about packages and version used in this vignette). 
Although main data structures have been thought out and are meant to be compatible with other existing 
mature infrastructure in the Bioconductor project, changes may occur in the future. 
Current functionality will evolve and new one will be added. 
Although at an early stage, this package is released in the hope that it may foster  
new developments in proteomics data analysis within \R by providing a common infrastructure. 
Several package developers working with mass spectrometry and proteomics data met at the 
Bioconductor Developer Meeting Europe\footnote{\url{http://bioconductor.org/help/course-materials/2010/HeidelbergNovember2010/}} 
held in Heidelberg in November 2010, and agreed to combine efforts. 
This library is one attempt to do so.

\bigskip

>>>>

%% \Rpackage{MSnbase} is in an early development %%(package version \Sexpr{packageVersion("MSnbase")}, 
%% (see section \ref{sec:sessionInfo} for details about packages and version used in this vignette). 
%% Although main data structures have been thought out and are meant to be compatible with other existing 
%% mature infrastructure in the Bioconductor project, changes may occur in the future. 
%% Current functionality will evolve and new one will be added. 
%% Although at an early stage, this package is released in the hope that it may foster  
%% new developments in proteomics data analysis within \R by providing a common infrastructure. 
%% Several package developers working with mass spectrometry and proteomics data met at the 
%% Bioconductor Developer Meeting Europe\footnote{\url{http://bioconductor.org/help/course-materials/2010/HeidelbergNovember2010/}} 
%% held in Heidelberg in November 2010, and agreed to combine efforts. 
%% This library is one attempt to do so.

\Rpackage{MSnbase} is under active developed; current functionality is evolving and 
new features will be added. This software is free and open-source software. 
If you use it, please support the project by citing it in publications:

\begin{quote}
  Laurent Gatto and Kathryn S. Lilley. \textit{MSnbase - an R/Bioconductor 
    package for isobaric tagged mass spectrometry data visualization,
    processing and quantitation.} Bioinformatics 28, 288-289 (2011).
\end{quote}
